---
title: "Praccomp Final Project"
author: "Diondre Hicks and Zach Smarr"
date: "2022-11-22"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reading the data into the environment
```{r}
df <- read.csv("Medicinal_plants_COVID-19_Cusco_English.csv")
df
#install.packages("ggplot2")
```
## Creating barplot for people who used plants for prevention
```{r}
barplot(table(df$Use.for.prevention), main= "Plants Used for Prevention", ylab="Number of People", xlab ="Responses", col = c("red", "blue"))
table(df$COVID.19.diagnosis)
table(df$Use.for.prevention, df$COVID.19.diagnosis)
```
## Barplot of Med Plants used for treatment
```{r}
barplot(table(df$Use.for.treatment), xlab="Responses", ylab="Nubmer of Patients",main = "Patients who Used for Treatment", col=c("red","blue"), )
table(df$Use.for.treatment)
table(df$COVID.19.diagnosis)
table(df$Use.for.treatment, df$COVID.19.diagnosis)
```
## Created 3D piechart depicting Effectiveness of Med Plant Prevention
```{r}
#install.packages("plotrix")
library(plotrix)
table(df$Use.for.prevention, df$COVID.19.diagnosis)
data <- c(1232, 169)
piepercent3D <-round(100*data/sum(data), 1)
lab <- c("Tested Negative for Covid", "Tested Positive for Covid")
pie3D(data, labels= piepercent3D, labelcex = .6, main= "Used Medical Plants for Prevention")
legend("topright", c("Negative", "Positive"), cex=.8, fill = c("red", "light blue"))
```

## Piechart showing Treatment of COVID-19 with plants
```{r}
#install.packages("plotrix")
library(plotrix)
table(df$Use.for.treatment)
x <- c(506, 1241)
piepercent <- round(100*x/sum(x), 1)
pie(x, labels= piepercent, main= "Covid-19 Treated With Medicinal Plants", col= rainbow(length(x)))
legend("topright", c("No", "Yes"), cex = .8, fill = rainbow(length(x)))
```

## Histogram showing Age distribution of study
```{r}
hist(table(df$Age), breaks=6)
lines(density(table(df$Age)))
```

## Histogram of Age Distribtion who Used Plants for Prevention
```{r}
#df_preventionY <- 
hist(table(subset(df, Use.for.prevention == "Yes", select = "Age")))
#df_preventionY
```

## Histogram For no Plant usage for Prevention
```{r}
hist(table(subset(df, Use.for.prevention == "No", select = "Age")))
```



